---
title: "Movie"
author: "Prateek Nayan"
date: "7/13/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse,shiny, dplyr, tidyr, htmltools, plotly, shinyWidgets, lubridate, leaflet,stringr,ggrepel,corrplot,GGally)
```

```{r}
movie = read.csv("movie_metadata.csv")
str(movie)
sum(duplicated(movie))
movie = movie[!duplicated(movie),]
str(movie)
colSums(sapply(movie, is.na))
movie <- movie[!is.na(movie$gross), ]
movie <- movie[!is.na(movie$budget), ]

movie$movie_title = gsub("Â", "", as.character(factor(movie$movie_title)))
str_trim(movie$movie_title, side = "right")
```



```{r Tab1}
movie = na.omit(movie)

movie$profit = ( movie$gross - movie$budget)
movie$ROI = (movie$profit/movie$budget) * 100

table(movie$country)

levels(movie$country) <- c(levels(movie$country), "Outside-USA")
movie$country[(movie$country != 'USA')] <- 'Outside-USA' 
movie$country <- factor(movie$country)
table(movie$country)

t = table(movie$ROI, movie$country)
barplot(t,main="USA vs Outside USA",xlab = "country", ylab = "ROI")
```

Question 1: To know if movie location has an impact on the profitability of the movie, I tried to do a barplot of US Vs Non-US countries. If we observe the country column most of the countries are from US and hence it is easier to distinguish countries as US and Non-US. From the plot it can be inferred that ROI% is more for countries in USA than in Non-USA. Yes, Movie location has an impact on profitability. Seeing the ROI% being significantly more for USA, it is better if more movies are produced inside USA
```{r Tab2}
library(dplyr)

AD = data.frame(Actor = movie$actor_1_name, Director=movie$director_name,Profit= movie$profit, ROI =movie$ROI)

AD%>% group_by(AD$Actor,AD$Director)%>% summarise(c = (ROI))%>% arrange(desc(c))

```
Question 2: "Micah Sloat" and "Orean Peli" - Actor-Director combination delivered the most profitable movies during the time period covered in this dataset based on ROI%

```{r Tab3}
movie %>%
  plot_ly(x = ~title_year, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~director_name, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~movie_facebook_likes, y = ~imdb_score, mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~num_critic_for_reviews, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~duration, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~director_facebook_likes, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~profit, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~content_rating, y = ~imdb_score , mode = "markers", alpha = 0.7, type = "scatter")
```
Question 3 : The following variables are seen to influence the IMDB score the most - Budget, Title_year, Duration, Gross.

Budget : It can be notied that as Budget increased, IMDB score has increased too.
Duration : If the duration of the movie was optimum like within 2 hrs, IMDB rating was found to be high. If the duration of the movie was long (>3 hours) IMDB rating was found to be slightly lower.
Title_Year : We can notice that all the movies were directed after the yeat 1990

```{r Tab4}
movie %>%
  plot_ly(x = ~movie_facebook_likes, y = ~budget, mode = "markers",alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~(actor_1_facebook_likes), y = ~(budget), mode = "markers",alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~(actor_2_facebook_likes), y = ~(budget), mode = "markers",alpha = 0.7, type = "scatter")

movie %>%
  plot_ly(x = ~(actor_3_facebook_likes), y = ~(budget), mode = "markers",alpha = 0.7, type = "scatter")

#Heatmap
ggcorr(movie[,c("movie_facebook_likes","actor_1_facebook_likes","actor_2_facebook_likes","actor_3_facebook_likes","budget")])

```

Question 4: To infer if Facebook likes for the movie and/or actors depend on the budget of the movie i used a heatmap. We can infer that there 0 or no corelation between these variables and budget.

```{r Shiny App}


ui <- fluidPage(
  titlePanel("Movie dataset"),
  
  # Sidebar layout with a input and output definitions 

    # Main panel for displaying outputs
    mainPanel(
      tabsetPanel(
        tabPanel("Usa vs Non Usa - profitability", 
                 plotOutput("Frequency")),
        
        tabPanel("Actor-Director most profit", 
                selectInput(
                  inputId = "Number", 
                  label= "No of movies",
                  choices = 1:10
                ),
                 tableOutput(outputId = "TableOutput")),
        tabPanel("variables influencing IMDB rating",
                plotOutput("budget"),
                plotOutput("duration"),
                plotOutput("year")
                ),
        tabPanel("Budget",
                plotOutput("fact")
                )
      )
    )
)

server <- function(input, output) {

  # US vs Non-Us
  output$Frequency <- renderPlot({
                    barplot(t,main="USA vs Outside USA",xlab = "country", ylab = "ROI")
    })
  
#Most Profitable Movies
  output$TableOutput<-renderTable({
   p = AD%>% group_by(AD$Actor,AD$Director)%>% summarise(c = (ROI))%>% arrange(desc(c))
   p$number = 1:3768
   p[1:input$Number,]
  })
  
#Factors affecting IMDB rating
  output$budget<-renderPlot({
            ggplot(movie, aes(x=movie$budget, y=movie$imdb_score))+geom_point()
    
  })
  
  
  output$duration = renderPlot({
            ggplot(movie, aes(x=movie$duration,y=movie$imdb_score))+geom_point()
  
  })
  
  output$year = renderPlot({
            ggplot(movie, aes(x=movie$title_year,y=movie$imdb_score))+geom_point()
  
  })

 #Budget vs facebook likes for actor and movies
    output$fact<-renderPlot({
     
ggcorr(movie[,c("movie_facebook_likes","actor_1_facebook_likes","actor_2_facebook_likes","actor_3_facebook_likes","budget")])
    
  })
  
}

# Create a Shiny app object
shinyApp(ui = ui, server = server)

```

